Real-Time Activity Classification by Match Filtering using Body-Worn Accelerometers

### 2016-06-18 notes/paper/paper.tex
Incremental changes to the paper.

If we let $\textbf{a} = \{a_i\}_{i=0}^{N}$ represent our demeaned acceleration data over a specified time window in three dimensions then the covariance matrix of our acceleration data is represented by the real-symmetric $3x3$ matrix $Q = \textbf{a} \textbf{a}^T$.
The resulting eigen vectors of this matrix are orthogonal and point in the directions where the data varies most [cite from some textbook here].
By projecting our data on the plain defined by the two most dominant eigen vectors, we effectively reduce our representation of our data to two dimensions.

To compute the matched-filter output for two dimensions, we generalize \eqref{matched_filter_eq} by the following:
%
\begin{equation} \label{cross_correlation_eq_2}
\widehat{(\textbf{x}^{1,2} \star \textbf{y}^{1,2})}_k^2 = \frac{(\textbf{x}^1 \star \textbf{y}^1)_k + (\textbf{x}^2 \star \textbf{y}^2)_k}{||[ \textbf{x}^1, \textbf{x}^2 ]|| \ || [ \widetilde{\textbf{y}}_k^1, \widetilde{\textbf{y}}_k^2 ] || },
\end{equation}
%
\begin{equation} \label{matched_filter_eq_2}
MF_{\textbf{x}}^2(\textbf{y}) := \underset{k \in [0, M-N)}{max} \left \{\widehat{(\textbf{x} \star \textbf{y})}^2_k \right \}
\end{equation}
%
for $ k = 0,1,...,N-M-1 $.\\
%
This works because both dimensions are always in phase with each other for a given activity
\subsection{Decimation}
Decimation is the first step applied to our data before any additional processing takes place.
Decimation is a process of reducing the sampling rate of a signal.
The process consists of filtering to mitigate any possible aliasing distortion effects followed by a downsampling.
There is a tradeoff between performance and throughput when we decimate our signal, therefore, we use decimation solely for the purpose of improving our throughput.

@@

If $\textbf{t} = \{t_k\}_{k=0}^{N_t}$ is our training set over $N_t$ data points, we define a collection of subsets $X$ of $\textbf{t}$:
%
\begin{equation} \label{X_subsets_of_training_eq}
X := \left \{ \{t_k\}_{k=p}^{p+M-1} | p=mI \right \}
\end{equation}
%
and $Y$ of $\textbf{t}$:
%
\begin{equation} \label{Y_subsets_of_training_eq}
Y := \left \{ \{t_k\}_{k=p}^{p+N-1} | p=nI \right \}
\end{equation}
%
where $M \leq N$, $I$ is a positive, fixed integer, and $(n,m) \in \mathbb{Z}^2$ where $(m,n)$ vary such that $0 \leq (m,n)I$ and $(m,n)I + (M,N) - 1 \leq N_t$. Then we can determine the representative signal $\textbf{s} \in X$ for our activity that satisfies the condition:
%
\begin{equation} \label{s_condition}
\sum_{y \in Y}MF_{\textbf{s}}(\textbf{y}) \geq \sum_{y \in Y}MF_{\textbf{x}}(\textbf{y}) \quad \forall \textbf{x} \in X
\end{equation}

>>>>

If we let $\textbf{a} = \{a_i\}_{i=0}^{N}$ represent our demeaned acceleration data over a specified time window in three dimensions then the covariance matrix of our acceleration data is represented by the real-symmetric $3 \times 3$ matrix $Q = \textbf{a} \textbf{a}^T$.
The resulting eigen vectors of this matrix are orthogonal and point in the directions where the data varies most [cite from some textbook here].
By projecting our data on the plain defined by the two most dominant eigen vectors, we effectively reduce our representation of our data to two dimensions.

To compute the matched-filter output for two dimensions, we generalize \eqref{matched_filter_eq} by augmenting our reference and data with both dimensions appropriately for normalization and adding together the cross correlations as:
%
\begin{equation} \label{cross_correlation_eq_2}
\widehat{(\textbf{x}^{1,2} \star \textbf{y}^{1,2})}_k^2 = \frac{(\textbf{x}^1 \star \textbf{y}^1)_k + (\textbf{x}^2 \star \textbf{y}^2)_k}{||[ \textbf{x}^1, \textbf{x}^2 ]|| \ || [ \widetilde{\textbf{y}}_k^1, \widetilde{\textbf{y}}_k^2 ] || },
\end{equation}
%
for $ k = 0,1,...,N-M-1 $.\\
%
\begin{equation} \label{matched_filter_eq_2}
MF_{\textbf{x}}^2(\textbf{y}) := \underset{k \in [0, M-N)}{max} \left \{\widehat{(\textbf{x} \star \textbf{y})}^2_k \right \}
\end{equation}
%
This works because both dimensions are always in phase with each other for any given activity which means that the match will happen in sinc.
%
\subsection{Decimation}
Decimation is the first step applied to our data before any additional processing takes place.
Decimation is a process of reducing the sampling rate of a signal.
The process consists of filtering to mitigate any possible aliasing distortion effects followed by a downsampling.
There is a tradeoff between performance and throughput when we decimate our signal, therefore, we use decimation solely for the purpose of improving our throughput.

@@

If $\textbf{t} = \{t_k\}_{k=0}^{N_t}$ is our training set over $N_t$ data points, we define a collection of subsets $X$ of $\textbf{t}$:
%
\begin{equation} \label{X_subsets_of_training_eq}
X := \left \{ \{t_k\}_{k=p}^{p+M-1} | p=mI \right \}
\end{equation}
%
and $Y$ of $\textbf{t}$:
%
\begin{equation} \label{Y_subsets_of_training_eq}
Y := \left \{ \{t_k\}_{k=p}^{p+N-1} | p=nI \right \}
\end{equation}
%
where $M \leq N$, $I$ is a positive, fixed integer, and $(n,m) \in \mathbb{Z}^2$ where $(m,n)$ vary such that $0 \leq (m,n)I$ and $(m,n)I + (M,N) - 1 \leq N_t$. Then we can determine the representative signal $\textbf{s} \in X$ for our activity that satisfies the condition:
%
\begin{equation} \label{s_condition}
\sum_{y \in Y}MF^2_{\textbf{s}}(\textbf{y}) \geq \sum_{y \in Y}MF^2_{\textbf{x}}(\textbf{y}) \quad \forall \textbf{x} \in X
\end{equation}
